Follow-up Samples

### 2017-01-11 submission/manuscript_outline_20161024.Rmd
update tables to be loaded

# initial microbiome and FIT description data 
change_summary <- read.csv('../results/tables/change_theta_fit_summary.csv', header = T, row.names = 1)
alpha_summary <- read.csv('../results/tables/alpha_table_summary.csv', header = T, row.names = 1)
beta_summary <- read.csv('../results/tables/beta_diver_summary.csv', header = T, row.names = 1)
time_pvalues <- read.csv("../results/tables/time_pvalues.csv", header = T, row.names = 1)

# training of model data
model_train_summary <- read.csv('../results/tables/ROC_model_summary.csv', header = T)
model_test_AUC_summary <- read.csv('../results/tables/auc_summary.csv', header = T, row.names = 1)
imp_model_vars <- read.csv('../results/tables/rf_wCV_imp_vars_summary.csv', stringsAsFactors = F, header = T)
rf_otu_tax <- read.csv('../results/tables/rf_otu_tax.csv', stringsAsFactors = F, header = T, row.names = 1)
rf_lowest_ID <- createTaxaLabeller(rf_otu_tax)

# model prediction and adjustment performance
IF_model_wilcox_paired_summary <- read.csv('../results/tables/all_models_wilcox_paired_pvalue_summary.csv', header = T)
confusion_summary <- read.csv('../results/tables/confusion_summary.csv', header = T, row.names = 1)
follow_up_prob_summary <- read.csv('../results/tables/follow_up_probability_summary.csv', header = T)
followup_cm <- read.csv('../results/tables/followup_confusion_matrix.csv', header = T, row.names = 1)
initial_cm <- read.csv('../results/tables/initial_confusion_matrix.csv', header = T, row.names = 1)
roc_pvalues <- read.csv('../results/tables/roc_pvalue_summary.csv', header = T, row.names = 1)

# Predictive of both initial and follow up and in lesion model
pvalue_common_imp_vars <- read.csv('../results/tables/pvalue_common_imp_vars.csv', header = T, row.names = 1)

# Results of CRC Bacteria
pvalue_adn_crc_summary <- read.csv('../results/tables/adn_crc_maybe_pvalue_summary.csv', header = T, row.names = 1)

@@

bacterial microbiome; colorectal cancer; polyps

>>>>

# initial microbiome and FIT description data 
change_summary <- read.csv('../results/tables/change_theta_fit_summary.csv', header = T, row.names = 1)
alpha_summary <- read.csv('../results/tables/alpha_table_summary.csv', header = T, row.names = 1)
beta_summary <- read.csv('../results/tables/beta_diver_summary.csv', header = T, row.names = 1)
time_pvalues <- read.csv("../results/tables/time_pvalues.csv", header = T, row.names = 1)
all_OTU_pair_wilcox <- read.csv("../results/tables/OTU_paired_wilcoxson_test.csv", header = T)

# Lesion Model (Full)
lesion_top10_varsMDA <- read.csv('../results/tables/lesion_model_top_vars_MDA_Summary.csv', header = T)
lesion_imp_vars <- read.csv('../results/tables/rf_otu_tax.csv', header = T, row.names = 1)
lesion_AUC_run_summary <- read.csv('../results/tables/ROC_model_summary.csv', header = T)

# Lesion Model (Reduced)
reduced_lesion_AUC_run_summary <- read.csv('../results/tables/reduced_IF_ROC_model_summary.csv', header = T)

# IF Model (Full)
IF_top10_varsMDA <- read.csv('../results/tables/IF_model_top_vars_MDA_Summary.csv', header = T)
IF_imp_vars <- read.csv('../results/tables/if_rf_otu_tax.csv', header = T, row.names = 1)
IF_AUC_run_summary <- read.csv('../results/tables/IF_ROC_model_summary.csv', header = T)

# IF Model (Reduced)
reduced_IF_AUC_run_summary <- read.csv('../results/tables/reduced_IF_ROC_model_summary.csv', header = T)

# All model information
all_probs_paired_wilcox <- read.csv('../results/tables/all_models_wilcox_paired_pvalue_summary.csv', header = T, stringsAsFactors = F)
all_pred_stat_summary <- read.csv('../results/tables/all_models_summary_info.csv', header = T, stringsAsFactors = F)
all_confu_matrix <- read.csv('../results/tables/all_models_confusion_summary.csv', header = T, stringsAsFactors = F)

# Common Variable Info
common_vars_summary <- read.csv('../results/tables/pvalue_IF_lesion_common_imp_vars.csv', header = T, row.names = 1)

@@

bacterial microbiome; colorectal cancer; polyps; FIT; detection; risk factors
